Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
partial draft of conclusion

\section{Conclusion}
\label{sec:conclusion}
expected dependency pair matching gets at something new

troubling area: speed of analysis -- current implementation requires
running a complete n-best parser

possible use: as a late-pass evaluation, to identify how systems
perform overall

future work:  explore ways to get at syntactic information without
the expense of a full parser:
\begin{itemize}
\item this work moves from an LFG parser (Owczarzak) to the
  substantially simpler and more robust Charniak system - keep going
  and look at simpler partial-parsing approaches (forests?)
\item conversely: how important is it that the parses be of
  high-quality?
\end{itemize}

>>>>

question: this is kind of like the $\mu_{PR}[\cdot]$ --- seems like it
also doesn't work so well. compare to EDPM as-is

talk about why EN is < EDPM (is it?)

\section{Conclusion}
\label{sec:conclusion}
In this research, we explore dependency pair match (DPM) a family of
syntactically-oriented measures.  Through a corpus of human judgments,
we settle on EDPM, a member of that family with promising predictive
power.  When tested against correlations with HTER, we find that EDPM
is as good a predictor of HTER as current measures BLEU$_4$ and TER,
and --- depending on the language and genre --- often better.

Several areas of future work are open to us. Using these syntactic
techniques may be possible as a late-pass evaluation, to identify how
candidate translation systems are performing overall.  Alternatively,
the various tree-decompositions of the DPM family could be used as
system diagnostics, by looking at relative quality of these component
scores compared to those of an alternative candidate system.

Another interesting research area is in the quality of the parser.  In
this work, we demonstrated that the
\inlinecite{charniak-johnson:2005:ACL} PCFG parser could serve in
place of the LFG parser used in
\inlinecite{owczarzak07labelleddepseval}. PCFG parsers, however, are
fairly easily adaptable to another domain. One interesting research
direction explores the intersection of genre (and genre-mismatch),
parser quality, and prediction of human performance. Another
consideration is the speed of the parser: parse time currently takes
much, much longer than BLEU, TER, or other word-based measures. We are
interested in the trade-offs --- if any --- among parse quality,
speed, and predictive power as a translation metric.  One possibility,
for example, is to store packed forests \cite{huang08packedforests}
rather than generating an $n$-best list only to sum across it again in
calculating the expectation.

TO DO: parting words
